% !TEX program = XeLaTeX

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{Klement_Resume}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{Tan De Ning, Klement}{
  \href{mailto:klementtan@gmail.com}{klementtan@gmail.com} |
  \urlstyle{same}\href{https://klementtan.com}{klementtan.com} |
  \href{https://github.com/klementtan}{github.com/klementtan} |
  \urlstyle{same}{+65 92399913} 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{minipage}[t]{1\textwidth} 

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %     EXPERIENCE
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \section{Education} 

  \runsubsection{National University of Singapore}
  \location{| Aug 2018 - May 2022} 
  Bachelor of Computing in Computer Science and Bachelor of Science in Applied Mathematics.
  \sectionsep

    \section{Work Experience}
    \runsubsection{Jump Trading}
    \descript{| Core Dev (C++)}
    \location{Software Engineering Intern | May 2022 - July 2022}
    \vspace{\topsep} % Hacky fix for awkward extra vertical space
    \begin{tightemize}
      \item Incoming Summer 2022 intern in the Core Development (C++) team in Jump Trading.
    \end{tightemize}
    \sectionsep

    \runsubsection{Squarepoint Capital}
    \descript{| Order Gateway}
    \location{Software Engineering Intern | Jan 2022 - May 2022}
    \begin{tightemize}
    \item Detected anomalies on the Order Gateway by implementing a post processor that calculates the gateway's latency in real time.
    \item Design and develop a resource efficient services that tracks continuously gateway resource usage.
    \item Tech Stack: {\bf C++} \textbullet{} {\bf Python} \textbullet{} {\bf Elastic Search}
    \end{tightemize}
    \sectionsep

    \runsubsection{Google}
    \descript{| Google Pay Client Infra}
    \location{Software Engineering Intern | May 2021 - Aug 2021}
    \begin{tightemize}
    \item Decreased the time taken to detect accessibility issues by {\bf 95\%} an automated crawler that detects accessibility issues.
    \item Led project from end to end by designing the architecture, implementing code, and developing processes for other teams to incorporate the tool into their workflow.
    \item Tech Stack: {\bf Flutter} \textbullet{} {\bf Bazel} \textbullet{} {\bf Java}
    \end{tightemize}
    \sectionsep


    \runsubsection{Ninja Van} \\
    \location{Software Engineering Intern | Dec 2020 - May 2021}
    \begin{tightemize}
    \item Oversaw the design and implementation of a search service that aggregates data from different multiple micro-services.
    \item Accomplished scalability by leveraging the asynchronous event-based system.
    \item Tech Stack: {\bf Play Framework} \textbullet{} {\bf MySQL} \textbullet{} {\bf Kafka} \textbullet{} {\bf Protocol Buffer} 
    \end{tightemize}
    \sectionsep

    \runsubsection{Xfers} \\
    \location{Software Engineering Intern | May 2019 - Nov 2019}
    \begin{tightemize}
    \item 
      Led the creation of an API documentation generator that decreases client integration time by {\bf50\%}. 
    \item
      Initiated and led the implementation of customized error codes that reduce the time taken to identify bugs by { \bf 80\% }.
    \item Tech Stack: {\bf Ruby on Rails} \textbullet{} {\bf React} \textbullet{} {\bf Open API Specification}
    \end{tightemize}
    \sectionsep

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     Projects
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Projects}
    \runsubsection{Bitcoin}
    \descript{| \href{https://github.com/bitcoin/bitcoin/pulls?q=+is\%3Apr+author\%3Aklementtan+}{github.com/bitcoin/bitcoin}}
    \begin{tightemize}
    \item Improved user experience of -getinfo CLI command; revamped the return format to include colours and progress bar. PRs: \href{https://github.com/bitcoin/bitcoin/pull/21832}{\#21832} \href{https://github.com/bitcoin/bitcoin/pull/22547}{\#22547} \href{https://github.com/bitcoin/bitcoin/pull/22959}{\#22959}
    \item Detected and resolved bugs in the code base. PRs: \href{https://github.com/bitcoin/bitcoin/pull/24371}{\#24371} \href{https://github.com/bitcoin/bitcoin/pull/21718}{\#21718}
    \item Executed quality assurance testing and code review on various other contributors' pull requests.
    \item Tech Stack: {\bf c++}
    \end{tightemize}
    \sectionsep

    \runsubsection{Static Analyzer in C++17}
    \descript{  }
    \begin{tightemize}
      \item Developed a highly performant static analyzer for the SIMPLE programming language in C++ 17.
      \item Implemented a recursive descent parser to construct an abstract syntax tree.
      \item Achieved low latency by implementing a custom memory arena allocator.
      \item Leveraged on templates to achieve compile time polymorphism and smart pointers for easy memory management.
    \end{tightemize}
    \sectionsep

    \runsubsection{C++ String}
    \descript{  }
    \begin{tightemize}
      \item Implemented std::string with short string and copy on write optimisation.
      \item Achieved 2x speedup over LLVM's implementation when copying long strings.
      \item You can view the project \href{https://github.com/klementtan/string_cpp}{here}
    \end{tightemize}
    \sectionsep

  \section{Technical Skills} 
  \vspace{\topsep} % Hacky fix for awkward extra vertical space
  \begin{tightemize}
    \item {\bf Languages}: Python \textbullet{} C++ \textbullet{} Java \textbullet{} Dart \textbullet{} Ruby \textbullet{} Javascript \textbullet{} Bash
    \item {\bf Technologies}: Bazel \textbullet{} Flutter \textbullet{} Elastic Search \textbullet{} Kafka \textbullet{} Ruby on Rails \textbullet{} React \textbullet{} Docker \textbullet{} pytest \textbullet{} MySQL/PostgresSQL \textbullet{} Git
    \end{tightemize}

  \end{minipage} 
  \end{document}  \documentclass[]{article}
